Cor Compare

### 2022-09-29 graphs_newt_snakes/corcompare.Rmd
looking more at the correlations and preping for the grid experiment

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library("reshape")
library(dplyr)

@@

all_cor_exp %>%
  group_by(group_exp) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)

@@

same GA should be differwent in the different experiments

@@

>>>>

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library("reshape")
library(dplyr)
library(ggside)
```

@@

all_the_means = all_cor_exp %>%
  group_by(group_exp) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)

all_the_means$exp <- str_split_fixed(all_the_means$group_exp, "5_", 3)[,3]

exclude_b <- all_the_means[which(all_the_means$exp!='B'),]
exclude_c <- all_the_means[which(all_the_means$exp!='C'),]

print("Anovas from mean of A and B")
res.aov2ab <- aov(name ~ exp, data = exclude_c[which(exclude_c$exp!='D'),])
summary(res.aov2ab)
print("Anovas from mean of A and C")
res.aov2ac <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='D'),])
summary(res.aov2ac)
print("Anovas from mean of A and D")
res.aov2ad <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='C'),])
summary(res.aov2ad)
print("Anovas from mean of C and D")
res.aov2cd <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='A'),])
summary(res.aov2cd)
```

@@

same GA should be different in the different experiments

@@

```{r, ggslide test}

ggplot(all_cor_exp) + 
  #geom_point(size = 2) +
  #geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=rep))+
  geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity")+
  #geom_xsidehistogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity") +
  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
  scale_ysidex_discrete(guide = guide_axis(angle = 45))
